Covariate analysis of MSSM reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-08-29 code/Rmd/MAYO_REPROCESSED.Rmd
Minor modifications

### Outlier Analysis
```{r outlier.analysis, cache = FALSE, fig.width = 10}
indToRemove = c("11311_CER", "1923_CER", "1923_TCX", "11396_TCX", "11294_TCX", "11408_TCX")

@@

# Store differential expression results
write.table(DE, file = 'MAYO_CBE_TCX_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MAYO_CBE_TCX_DiffExpression.tsv', 
                name = 'Differential Expression Results (BrainRegion.Diagnosis)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (estimated)                         |  `r ECOUNT_OBJ$properties$id`    |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Surrogate Variables                        |  `r SURR_OBJ$properties$id`      |
|  Residual Expression (for eQTL)             |  `r eEXP_OBJ$properties$id`      |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |

>>>>

### Outlier Analysis
```{r outlier.analysis, cache = FALSE, fig.width = 10}
indToRemove = c("11311_CER", "1923_CER", "1923_TCX", "11396_TCX", "11294_TCX", "11408_TCX",
                '1950_TCX', '1950_CER', '1925_TCX', '1957_CER')

@@

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
  write.table(file = 'MAYO_CBE_TCX_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MAYO_CBE_TCX_DiffExpression.tsv', 
                name = 'Differential Expression Results (BrainRegion.Diagnosis)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
# stopCluster(cl)
```
|  *Results*                                  |  *SynapseID*                     |
|  -----------------------------------------  |   ---------                      |
|  Covariates                                 |  `r COV_OBJ$properties$id`       |
|  Counts (raw)                               |  `r COUNT_OBJ$properties$id`     |
|  Counts (estimated)                         |  `r ECOUNT_OBJ$properties$id`    |
|  Counts (lcpm)                              |  `r LCOUNT_OBJ$properties$id`    |
|  Offset (for gene length and gc content)    |  `r OFFSET_OBJ$properties$id`    |
|  Design Matrix                              |  `r DM_OBJ$properties$id`        |
|  Surrogate Variables                        |  `r SURR_OBJ$properties$id`      |
|  Residual Expression (for eQTL)             |  `r eEXP_OBJ$properties$id`      |
|  Residual Expression (for network analysis) |  `r nEXP_OBJ$properties$id`      |
|  Differential Expression                    |  `r DEXP_OBJ$properties$id`      |

### 2017-08-29 code/Rmd/MSSM_REPROCESSED.Rmd
Minor modifications

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
  write.table(file = 'MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', name = 'Differential Expression Results (cogdx)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

>>>>

# Store differential expression results
rbindlist(all.diff.exp, use.names = T, fill = T, idcol = 'Model') %>%
  write.table(file = 'MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', sep = '\t', row.names=F, quote=F)
DEXP_OBJ = File('MSSM_FP_STG_PHG_IFG_DiffExpression.tsv', name = 'Differential Expression Results (BrainRegion.Diagnosis)', 
                parentId = CODE$properties$id)
annotations(DEXP_OBJ) = annotations(CODE)
annotations(DEXP_OBJ)$dataSubType = 'diffExp'
DEXP_OBJ = synStore(DEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
